### 2016-10-27 latex/input/experiments.tex
results section comparison to mRMR+SVM updated

Finally, Table \ref{tab:test-comp} compares CAMIL to the method used by Qin et al., mRMR + SVM. We use 23 patients in the test set here because that is what Qin et al. did \cite{qin041012}. We averaged the results of 10 trials in which we selected 23 patients randomly out of the 367 to serve as the test set, with the other 344 of the training set. Table \ref{tab:test-comp} shows that CAMIL significantly outperformed mRMR + SVM, with the H-BoW variant of CAMIL slightly outperforming the D-BoW variant. The results held for the original 23 patient test set used by Qin et al., where CAMIL H-BoW actually achieved 100\% accuracy.

The method used in the original paper is the only one tested here that is not an MIL method, and the only one that is not entirely unsupervised apart from the patient labels. Given that the methods from this paper were not de novo, it makes sense that they would outperform many of the unsupervised MIL methods. However, CAMIL still significantly outperformed the results reported in the original paper. We believe that this is due to the following reasons: (i) the clustering process puts similar contigs into groups that are useful features for the classifier, and (ii) instead of attempting to select the most significant features before performing classification, we allow the classifier itself to determine the most significant features from the entire pool of features.

>>>>

Table \ref{tab:test-comp} compares CAMIL to the method used by Qin et al., mRMR + SVM. We initially tested CAMIL on the same 23 patient test set that Qin et al. used, for which CAMIL H-BoW had 100\% accuracy and AUC, while mRMR + SVM had 0.81 AUC as reported by Qin et al. \cite{qin041012}. We know CAMIL is not 100\% accurate, so we validated it by averaging the results of 10 independent trials in which we selected 23 patients randomly out of the 367 to serve as the test set, with the other 344 of the training set. Table \ref{tab:test-comp} shows that CAMIL significantly outperformed mRMR + SVM on these trials, with the H-BoW variant of CAMIL slightly outperforming the D-BoW variant.

Unlike the other MIL methods, Qin et al. use reference genomes to inform their classifier, so it makes sense that their method performs better than the MIL methods that only use de novo techniques. However, CAMIL still significantly outperformed the results reported in the MGWAS paper. We believe that the primary reason for this is that Qin et al. relied on alignments of sequences to reference genomes and attempted to select the 50 most significant genes for the phenotype before building the classifier. There are two primary problems with this approach: (i) many microbes found in the gut do not exist in reference databases and would thus be unusable for their classifier, and (ii) by only using 50 genes to inform the classifier, a lot of potentially valuable data is left out. CAMIL avoids these issues by using as much data as can be assembled and not relying on reference databases. The tradeoff is that we don't know exactly what genes are being used by the classifier to form the decision boundary. We also believe that the clustering process of putting similar contigs into groups forms useful features for the classifier.
